\section{Project Plan}
\sffamily % Use sans-serif font for this section's text

This section outlines the high-level plan for the Automata Odoo ERP System Implementation project, including the overall timeline with specific dates, key phases, milestones, deliverables, and underlying assumptions, considering a Sunday-Thursday working week.

\subsection{High-Level Plan (Project Timeline)}
The project is planned to be executed over a period of approximately 41.2 weeks of active work, divided into distinct phases. The following table outlines the main activities, their durations, and planned schedule, with the project kick-off on May 15, 2025 and accounting for the Eid Aladha holiday (June 8-12, 2025):

% Updated column specification for the first column to allow wrapping
\begin{longtable}{@{} >{\RaggedRight\arraybackslash}p{0.45\linewidth} c l l @{}} 
\toprule
\textbf{Activity / Phase} & \textbf{Duration} & \textbf{Start Date} & \textbf{End Date} \\
\midrule
\endfirsthead
% Header for continued pages
\toprule
\textbf{Activity / Phase} & \textbf{Duration} & \textbf{Start Date} & \textbf{End Date} \\
\midrule
\endhead
% Footer
\bottomrule
\endfoot
% Last footer
\bottomrule
\endlastfoot

1. Project Planning and Scoping & 3.2 weeks (16 days) & May 15, 2025 & Jun 05, 2025 \\ % Adjusted
\addlinespace
2. Requirements Gathering and Analysis & 2 weeks & Jun 15, 2025 & Jun 26, 2025 \\ 
\addlinespace
3. System Design and Development & 2 weeks & Jun 29, 2025 & Jul 10, 2025 \\ 
\addlinespace
4. Data Migration & 2 weeks & Jul 13, 2025 & Jul 24, 2025 \\ 
\addlinespace
5. User Acceptance Testing (UAT) & 4 weeks & Jul 27, 2025 & Aug 21, 2025 \\
\addlinespace
6. Training and Support (Pre Go-Live) & 4 weeks & Aug 24, 2025 & Sep 18, 2025 \\
\addlinespace
7. Deployment and Go-Live & Event & Sep 21, 2025 & Sep 21, 2025 \\
\addlinespace
8. Monitoring and Evaluation (Post Go-Live Support) & 24 weeks & Sep 22, 2025 & Mar 05, 2026 \\ 
\end{longtable}
\textit{Note: The above timeline is based on the technical proposal (Version 1.1, April 2025). Dates assume a Sunday-Thursday working week, with Friday and Saturday as non-working days. Eid Aladha holiday (Jun 08-12, 2025) is accounted for.}

\subsection{Low-Level Plan}
This section details the main tasks within each project phase, identifies the primary responsible party, and outlines key deliverables and conclusion criteria. The detailed plan for each phase is provided in the referenced document.

\input{content/0502_low_level_plan.tex} % Replaced inline low-level plan with input command

\subsection{Initial Communication Plan}
This subsection outlines the planned communication activities and meetings throughout the project lifecycle. The detailed Communication Plan, including specific reporting templates, distribution lists, and meeting cadences for each phase, is provided in the referenced document. Regular and effective communication is key to project success.

\input{content/0503_initial_communication_plan.tex} % Replaced inline communication plan with input command

\subsection{Summary Milestone Schedule}
The following are the major planning milestones for this project, with estimated dates based on the revised timeline (Sunday-Thursday working week) and key communication events:
\begin{itemize}
    \item Project Kick-off Meeting Conducted: May 15, 2025
    \item Project Charter Approved: Jun 05, 2025
    \item Requirements Sign-off (Blueprint Approval): Jun 26, 2025 
    \item System Configuration and Data Migration Plan Approved: Jul 10, 2025 
    \item Data Migration to Production and UAT Environment Ready: Jul 24, 2025 
    \item UAT Completion and Sign-off: Aug 21, 2025
    \item Go/No-Go Decision for Deployment: Sep 18, 2025
    \item System Go-Live: Sep 21, 2025
    \item End of Hyper-care Support: Oct 16, 2025
    \item Project Closure Sign-off: Mar 05, 2026
\end{itemize}

\subsection{Project Deliverables}
The key deliverables for this project are detailed in the "Scope of Work" section (Section 4.2 Deliverables). These include, but are not limited to:
\begin{itemize}
    \item A fully configured and operational Odoo ERP system (Invoicing, Accounting, Inventory, Purchase, Sales modules) on Odoo Online.
    \item Migrated Master Data (Financial, Inventory, Procurement).
    \item Custom Reports as specified.
    \item System Design Documentation.
    \item Test Plans and UAT Sign-off.
    \item Training Materials and delivered Training Sessions.
    \item Go-Live and Post Go-Live Support.
    \item Project Closure Report.
\end{itemize}

\subsection{Project Risks and Mitigation Strategies}
A detailed Risk Register will be maintained throughout the project lifecycle. Initial high-level risks and potential mitigation strategies are outlined in the "Scope of Work" section (Section 4.3.1 Potential Risks). Key areas include scope creep, resource availability, data quality, user adoption, and technical issues. Mitigation will involve strict change control, proactive resource planning, thorough data validation, comprehensive training, and robust testing.

\subsection{Plan Assumptions}
The successful execution of this project plan is based on the assumptions detailed in the "Scope of Work" section (Section 4.4 Assumptions). These include, but are not limited to:
\begin{itemize}
    \item Full client commitment and active participation from Automata stakeholders.
    \item Availability and quality of data for migration.
    \item Timely decision-making and approvals from Automata.
    \item Adherence to the defined project scope.
    \item Organizational readiness for change and adoption of new processes.
\end{itemize}
Any deviation from these assumptions may impact the project timeline, scope, or budget, and will be addressed through the project's issue and change management processes.
\newpage